---
title: "Package Calendar by Emit Hvitfeldt"
author: "Dom Grisafe"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE}
# prints session info
details::details(object = sessioninfo::session_info(), summary = 'current session info')
```

#2019{.tabset}

##Day 1: Datalegreyar

https://www.hvitfeldt.me/pkgcal2019/1/

```{r}
# devtools::install_github('emitanaka/datalegreyar')

# get data for "Last Christmas" song
# remotes::install_github("PMassicotte/gtrendsR")
library(gtrendsR)
last_christmas <- gtrends("Last Christmas", time = "today 3-m")

# use the datafy() function to combine the values and the text
library(datalegreyar)
last_christmas_data <- datafy(
  values = last_christmas$interest_over_time$hits,
  text = "Last Christmas",
  ignore_space = FALSE
)

last_christmas_data

# pass the datafied object to fig() to render it in our document
# note: this only shows up in the html knitted document
datalegreyar::fig(last_christmas_data, size = 60)

# change the style, add limits
fig(last_christmas_data, size = 60, type = "gradient", xlabs = c("sep 1", "dec 1"))

# function for easy use
datalegreyar_factory <- function(text, size) {
  data <- datafy(
    values = gtrends(text, time = "today 3-m")$interest_over_time$hits,
    text = text,
    ignore_space = FALSE
  )
  fig(data, size = size, type = "gradient", xlabs = c("sep 1", "dec 1"))
}
datalegreyar_factory("Drummer Boy", size = 60) 
datalegreyar_factory("White Christmas", size = 50)
```

##Day 2: Glue

https://www.hvitfeldt.me/pkgcal2019/2/

```{r}
# install.packages("glue")

library(glue)

color <- "red"
glue("Santa packed a {color} present")

## Santa packed a red present
color <- c("red", "blue", "green")
glue("Santa packed a {color} present")

#This is commonly done by passing in a defined variable outside glue(), but remember that any expression can be passed to glue().
glue("`mtcars` has {nrow(mtcars)} rows and {ncol(mtcars)} columns")

# use the arguments .open and .close to redefine the borders
# useful if curly brackets used for something else
n <- 1000000000 # number of children
glue(.open = "<<", .close = ">>",
  "Santa uses the formula $<<n>>^{magic + love}$ to determine how much sugar to give to the elfs."
     )

# example with summary data
  library(dplyr)
  
  # make sumary dataset
  mtcars_summarized <- mtcars %>%
    group_by(cyl) %>%
    summarise(n = n(),
              min_wt = min(wt),
              max_wt = max(wt)) %>%
    mutate_all(round, digits = 2)
    mtcars_summarized
  
    # print sentence
    cat("`mtcars` has:\n")
    glue_data(mtcars_summarized,
              "{n} cars with {cyl} cylinders, with a weight range of {min_wt*1000}-{max_wt*1000} lbs")
```

##Day 3: Details

https://www.hvitfeldt.me/pkgcal2019/3/

```{r}
# install.packages("details")
```

The bare html code below creates a manual "details" drop down tag, without using R code.

<details>

 <summary>Secret list of names</summary>
 
 Aura
 
 Dona
 
 Danyelle
 
 Maribel
 
 Evonne
 
 Elly
 
 Joye
 
 Monet
 
 Donny
 
 Georgeanna
 
</details>

```{r}
library(details)
library(magrittr)

secret <- c("Madeline", "Tom", "Shavon", "Krystyna", "Callie",
            "Damon", "Shellie", "Bebe", "Candis", "Laure")
```

Now, this details package allows you to hide r code objects in "details" drop-down menus

```{r}
details(secret)
```

This is good for hiding session info

```{r}
sessioninfo::session_info() %>%
  details::details(summary = 'current session info')
```


##Dat 4: Carbonate

https://www.hvitfeldt.me/pkgcal2019/4/

This produces pretty image files of selected code, copied to your clipboard

```{r}
# install.packages("carbonate")
library(carbonate)

# copy some code to your clipboard
x <- carbon$new()

# this lets you check the code you have is what you wanted
x$code

# this opens a webpage in browser where there is a pretty image of your code, which can then be downloaded
x$browse()
```

